---
title: "Assignment 3"
author: "Annie Beyer and Caleb Aguiar"
date: "1/25/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1


```{r}
tide128_rev<-sum(detergent_DF$q_tide128*detergent_DF$p_tide128)
tide64_rev<-sum(detergent_DF$q_tide64*detergent_DF$p_tide64)
wisk64_rev<-sum(detergent_DF$q_wisk64*detergent_DF$p_wisk64)

tide128_per<-tide128_rev/(tide64_rev+wisk64_rev+tide128_rev)
tide64_per<-tide64_rev/(tide128_rev+wisk64_rev+tide64_rev)
wisk64_per<-wisk64_rev/(tide64_rev+tide128_rev+wisk64_rev)

total<-tide128_per+tide64_per+wisk64_per

library(psych)

describe(detergent_DF)

Product<-c("Tide 128","Tide 64","Wisk 64")
Revenue<-c(tide128_rev,tide64_rev,wisk64_rev)
Marketshare_Percent<-c(tide128_per,tide64_per,wisk64_per)

Marketshare_table<-data.frame(Product,Revenue,Marketshare_Percent)

Marketshare_table

```


Q1a: Table of marketshare (in percentage) and price statistics (in dollars)

+---------------+---------------+-------------+--------------+-----------+
| Product       | Marketshare   | Mean Price  | Median Price | Std. Dev |          
+===============+===============+=============+==============+===========+
| Tide 128 oz   |      56.9%    |   8.36      |    8.48      |  .76      |
+---------------+---------------+-------------+--------------+-----------+
| Tide 64 oz    |      26.3%    |   4.36      |    4.42      |  .40      |
+---------------+---------------+-------------+--------------+-----------+
| Wisk 64 oz    |      16.8%    |   4.07      |    4.19      |  .49      |
+---------------+---------------+-------------+--------------+-----------+

Q1b: Generate two new variables that capture the price gap between Tide 128 and Tide 64 and Wisk 64. Report the mean, median and std dev of the two price gap variables across store-weeks.

```{r}
detergent_DF$prc_gp_Tide_128_to_64<-detergent_DF$p_tide128-detergent_DF$p_tide64 

detergent_DF$prc_gp_Tide_64_to_Wisk_64<-detergent_DF$p_wisk64-detergent_DF$p_tide64 

aggregate(detergent_DF$prc_gp_Tide_128_to_64, by=list(Store = detergent_DF$store), FUN=median)

```





## Question 6

: Table of quantities sold and profits when Tide changes the price of Tide 64 and 128. Price changes are shown in percentages

+---------------+---------------+-------------+--------------+---------------+
| del_price_128 | del_price_64  | q_128       | q_64         | Total profits |          
+===============+===============+=============+==============+===============+
| 0.05          | 0.05          |             |              |               |
+---------------+---------------+-------------+--------------+---------------+
| -0.05         | -0.05         |             |              |               |
+---------------+---------------+-------------+--------------+---------------+
| 0.05          | -0.05         |             |              |               |
+---------------+---------------+-------------+--------------+---------------+
| -0.05         | 0.05          |             |              |               |
+---------------+---------------+-------------+--------------+---------------+
