---
title: 'Assignment 3'
author: "Annie Beyer & Caleb Aguiar"
date: "January 2021"
output: word_document
urlcolor: blue
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages('devtools')#Packages required
#devtools::install_github("ropensci/skimr")
#install.packages('arm')#to plot coefficients 

```

##Upload and Explore Data

```{r}
load(file = "Detergent.RData")
dt <- detergent_DF
library(skimr)
library(psych)
library(ggplot2)
library(arm)
library(broom)
library(knitr)
skim(dt)
head(dt)
```

## Question 1

# A

```{r}
#Make Revenue column for each product

dt$T128Revenue <- dt$q_tide128 * dt$p_tide128
dt$T64Revenue <- dt$q_tide64 * dt$p_tide64
dt$WiskRevenue <- dt$q_wisk64 * dt$p_wisk64

TotalRevenue <- sum(dt$T128Revenue) + sum(dt$T64Revenue) + sum(dt$WiskRevenue)

T128Rev <- (sum(dt$T128Revenue) / TotalRevenue) * 100
T64Rev <- (sum(dt$T64Revenue) / TotalRevenue) * 100
WiskRev <- (sum(dt$WiskRevenue) / TotalRevenue) * 100

TotalRevenue1 <- format(round(TotalRevenue, 2), nsmall = 2)
T128Rev1 <- format(round(T128Rev, 2), nsmall = 2)
T64Rev1 <- format(round(T64Rev, 2), nsmall = 2)
WiskRev1 <- format(round(WiskRev, 2), nsmall = 2)

Mean128 <- mean(dt$p_tide128)
Mean64 <- mean(dt$p_tide64)
MeanW <- mean(dt$p_wisk64)

SD128 <- sd(dt$p_tide128)
SD64 <- sd(dt$p_tide64)
SDW <- sd(dt$p_wisk64)

Med128 <- median(dt$p_tide128)
Medn64 <- median(dt$p_tide64)
MednW <- median(dt$p_wisk64)

library(data.table)
Marketshare = c(T128Rev1, T64Rev1, WiskRev1)
MeanPrice = c(Mean128, Mean64, MeanW)
MedianPrice = c(Med128, Medn64, MednW)
Std.Dev = c(SD128, SD64, SDW)
Product <- c("Tide 128 oz", "Tide 64 oz", "Wisk 64 oz")

MarketShare <- data.frame(Product, Marketshare, MeanPrice, MedianPrice, Std.Dev)

describe(dt)
                          
MarketShare            
```

+---------------+---------------+-------------+--------------+-----------+
| Product       | Marketshare   | Mean Price  | Median Price | Std. Dev |          
+===============+===============+=============+==============+===========+
| Tide 128 oz   |      56.9%    |   8.36      |    8.48      |  .76      |
+---------------+---------------+-------------+--------------+-----------+
| Tide 64 oz    |      26.3%    |   4.36      |    4.42      |  .40      |
+---------------+---------------+-------------+--------------+-----------+
| Wisk 64 oz    |      16.8%    |   4.07      |    4.19      |  .49      |
+---------------+---------------+-------------+--------------+-----------+


# B
Price Gap

```{r}
dt$PriceGap1 <- dt$p_tide128 - dt$p_tide64
dt$PriceGap2 <- dt$p_tide64 - dt$p_wisk64

MeanPG1 <- mean(dt$PriceGap1)
MeanPG2 <- mean(dt$PriceGap2)

SDPG1 <- sd(dt$PriceGap1)
SDPG2 <- sd(dt$PriceGap2)

MedPG1 <- median(dt$PriceGap1)
MedPG2 <- median(dt$PriceGap2)

MeanPriceGap = c(MeanPG1, MeanPG2)
MedianPriceGap = c(MedPG1, MedPG2)
Std.DevPriceGap = c(SDPG1, SDPG2)                  
PriceGap <- c("Tide128- Tide64", "Tide64 - Wisk64") 

PriceGap <- data.frame(PriceGap, MeanPriceGap, MedianPriceGap, Std.DevPriceGap)

PriceGap 
```

+---------------+---------------+-------------+-----------+
| PriceGap      | MeanPriceGap  | MedianPrGap | Std. Dev  |          
+===============+===============+=============+===========+
| Tide128-Tide64|   3.9877679   |  4.094000   |  0.8705   | 
+---------------+---------------+-------------+-----------+
| Tide64 -Wisk64|   0.3034887   |  0.260714	 |  0.5859   |
+---------------+---------------+-------------+-----------+


# C
Histograms
```{r}
par(mfrow=c(1,2))#Set the plotting area into a 1*2 array

#Set axis to the same for better comparison
hist(dt$PriceGap1, freq = F, col = "steelblue", breaks = 50, xlab = "Price Gap 1 ($)", main = "Price Gap of Tide 128 - Tide 64",
     xlim = c(-3,8))
hist(dt$PriceGap2, freq = F, col = "orange", breaks = 50, xlab = "Price Gap 2 ($)", main = "Price Gap of Tide 64 - Wisk 64",xlim = c(-3,8))

par(mfrow=c(1,1))
```


# D
Discussion:
What do you learn from the price gap histograms and summary statistics for your analysis above? 

Examining the revenue market share, Tide 128oz is about double the price, and double the amount of revenue of Tide 64oz. 

This would suggest that the number of purchases made of each product is the same.

Tide 64 is more expensive than Wisk 64 on average.

The variability between Tide 128 and Tide 64 is less than the variability between Tide 64 and Wisk 64. 

Is there enough variation in the price gaps across stores and weeks to estimate the cross price elasticities between the two Tide pack sizes and Wisk 64?

Yes, there is enough variation between each scenario. 

## Question 2

# A 
Sales velocity for Tide 128 and Tide 64

```{r}
dt$svelocity128 <- (dt$q_tide128/dt$acv)
dt$svelocity64 <- (dt$q_tide64/dt$acv)

SalesVelocity128 <- sum(dt$svelocity128)
SalesVelocity64 <- sum(dt$svelocity64)

SalesVelocity128
SalesVelocity64
```

# B
Discussion:
What is the purpose of dividing unit sales by ACV to construct the dependent variable?


The ACV is a measure of how large the store is. By dividing by ACV, this allows us to normalize the data so we can compare the two products equally. We would expect a larger store to be more sensitive to price changes, as customers are more interested in price at a large store and have more options to substitute with, while customers at a small store are more likely to prioritize the convenience of the location and have less of a selection. Additionally, not all stores may sell each product every single week (whether that is due to operational supply difficulties, a lack of data recording, etc...)


# C
Log linear demand model 
```{r}
lm128 = lm(log(svelocity128) ~ log(p_tide128)+log(p_tide64) + log(p_wisk64), data = dt)
lm64 = lm(log(svelocity64) ~ log(p_tide128)+log(p_tide64) + log(p_wisk64), data = dt)

summary(lm128)
summary(lm64)

lm128_coef<- summary(lm128)$coefficients
lm64_coef<-summary(lm64)$coefficients#Lets graph these coefficients so we can see all these at a glance

pe_graph<-c(lm64_coef[2:3,1],lm128_coef[2:3,1])
pe_graph

barplot(pe_graph, main = "Price Elasticity", xlab = "Tide64's price elasticities              Tide128's price elasticities", col = rainbow(4), names.arg = c('Cross','Own', 'Own','Cross' ))

```


# D
Discussion:
Discuss whether the demand estimates (own and cross price elasticities) make sense. Are the magnitudes and signs of the estimated parameters as you would expect? 

OwnPE_128 = -4.59 Elastic, negative
OwnPE_64 = -3.74 Elastic, negative

CrossPE_128 = 0.31 Inelastic, positive. This is similar to addictive substances
CrossPE_64 = 1.28 Elastic
Cross_PE_128 & Wisk = 0.15 Inelastic, positive
Cross_PE_64 & Wisk = -0.87 Inelastic, negative

This regression shows that Tide128 and Tide64 are highly elastic, and there cross price elasticities are also elastic, but not as much. This suggests that as Tides own price increases, it's demand goes down by a lot and Tide 64's demand increases a little as well as the demand for Wisk, but not as much. However, when Tide 64's own price increases, its demand decreases, and Tide128 demand increases but only slightly. However, Wisk's demand decreases.

This does not make a lot of sense, because their price gap is sometimes at zero, and if that is the case customers are going to be falling over themselves to buy the Tide128 and not bother with Tide64. We need to examine if there is something going on here, is there more affluent locations where Tide64 is selling the same as Tide128 at a lower income area, or is there a seasonal element where people buy more Tide when they wash more clothes from sweating.


## Question 3

# A
Time Trend 

```{r}
dt$week<-as.integer(dt$week)
lm128_B <- lm(log(svelocity128) ~ log(p_tide128)+log(p_tide64) + log(p_wisk64) +  week, data = dt)
lm64_B <- lm(log(svelocity64) ~ log(p_tide128)+log(p_tide64) + log(p_wisk64) + week, data = dt)

lm128_Ba<-tidy(lm128_B) 
lm64_Ba<-tidy(lm64_B)

kable(lm128_Ba[c(1:3),], digits = 4)
kable(lm64_Ba[c(1:3),], digits = 4)

summary(lm128_B)
summary(lm64_B)


```

# B
Discussion:
Explain why adding a time trend is important here. Discuss whether the demand estimates now make sense. Is there an improvement over the model specification in question 2?

The demand estimates have changed, but only slightly. Not enough to now make sense.

Time trend is extremely important, once we accounted for seasonal trends, it improves the previous model immensely. This makes sense, since the purchase of detergent is likely to be driven by weather(depends on the location, but think about people spending alot of time outside vs inside would change the rate at which the product is used). It is important not to try to build too many assumptions into this. Tide128 is a product that may take a few weeks to consume, and so if there is a seasonal effect driving its consumption there will be a lag effect. The big takeaway is that incorporating the week that the detergent was purchased into our model we get a more accurate model.

See the table below for a comparison of the multiple R squared values. Once we implemented dummy variables for time, our model was able to capture between roughly 8-10% more of the variation.

+-------------------+---------------+-------------------+-----------------+
| Tide64 Linear-Log | Tide64 w/Time | Tide128Linear-Log | Tide 128 w/Time |         
+===================+===============+===================+=================+
| Adj.R^2  0.2217   | 0.3609        | 0.266             | 0.2898          | 
+-------------------+---------------+-------------------+-----------------+

## Question 4

# A

```{r}
library(dplyr)
detergent_promos <- dt %>% select(week, promoflag) %>% 
  filter(promoflag == 1)

totalweeks<-length(unique(dt$week))

promoweeks<-length(unique(detergent_promos$week))

store_week_fraction <- paste(promoweeks,totalweeks, sep = '/')

store_week_fraction #Did we lose some data, there isn't the expected 300 weeks.

sum(dt$promoflag)

detergent_DF_2 = subset(detergent_DF, promoflag != 1)

```


# B

```{r}
detergent_DF_2$svelocity128 <- (detergent_DF_2$q_tide128/detergent_DF_2$acv)
detergent_DF_2$svelocity64 <- (detergent_DF_2$q_tide64/detergent_DF_2$acv)

SalesVelocity128_B <- sum(detergent_DF_2$svelocity128)
SalesVelocity64_B <- sum(detergent_DF_2$svelocity64)

lm128_C = lm(log(svelocity128) ~ log(p_tide128)+log(p_tide64) + log(p_wisk64) +  week, data = detergent_DF_2)
lm64_C = lm(log(svelocity64) ~ log(p_tide128)+log(p_tide64) + log(p_wisk64) + week, data = detergent_DF_2)

summary(lm128_C)
summary(lm64_C)

lm128_Ca<-tidy(lm128_C)
lm64_Ca<-tidy(lm64_C)

kable(lm128_Ca[c(1:4),], digits = 4)
kable(lm64_Ca[c(1:4),], digits = 4)

```


# Discussion
Discuss whether the demand estimates (own and cross price elasticities) now make sense - is there an improvement over the specification in question 3? Provide some intuition for the change in the estimated own-price effects.


BEFORE: 
OwnPE_128 = -4.59 
OwnPE_64 = -3.74

CrossPE_128 = 0.31 
CrossPE_64 = 1.28
Cross_PE_128 & Wisk = 0.15 
Cross_PE_64 & Wisk = -0.87 

AFTER: 
OwnPE_128 = -3.5
OwnPE_64 = -1.7018

CrossPE_128 = 2.676
CrossPE_64 = -0.1158
Cross_PE_128 & Wisk = 0.7142
Cross_PE_64 & Wisk = -0.5189

The own price effects have decreased significantly, and also the gap between the two have increased as well. Now, Tide 128 is highly elastic while Tide 64 is mildly elastic. Additionally, as Tide 128 price increases, demand for Tide 64 decreases and demand for Wisk 64 increases. As Tide 64 prices increase, demand for Tide 128 increases and demand for Wisk decreases.It is still interesting that if demand increases for either Tide product, the demand for the opposite Tide product and for the Wisk product are not sharing the same sign (go in opposite directions).

## BEST GUESS?

## Question 5

Store Fixed Effect

# A

```{r}
lm128_D<-lm(log(svelocity128) ~ log(p_tide128)+log(p_tide64) + log(p_wisk64) + week + factor(store), data = detergent_DF_2)
lm64_D <- lm(log(svelocity64) ~ log(p_tide128)+log(p_tide64)+ log(p_wisk64) + week+ factor(store), data = detergent_DF_2)

library(broom)
library(knitr)

lm128_D <- tidy(lm128_D)
lm64_D <- tidy(lm64_D)



kable(lm64_D[c(1:4),], digits = 4)
#Comparison
kable(lm64_Ca[c(1:4),], digits = 4)

#Comparison
kable(lm128_D[c(1:4),], digits = 4)
kable(lm128_Ca[c(1:4),], digits = 4)




```

# B
Discussion:
Do the estimates of own and cross price elasticties reveal an improvement over the model specification
in question 4? 

Yes, the own and cross price elasticities decrease from Question 4's model to this model for Tide 64. For Tide 128, it's own price elasticity decreases and more noteably, the cross price elasticity for tide 64 changes sign from negative to positive, which finally makes more sense. This means that as prices for Tide 128 increase, the demand for Tide 64 increases only slightly and for Wisk 64 increases more significantly while the demand for Tide 128 decreases. As prices increase for Tide 64, demand for Tide 128 increases slightly while demand decreases slightly for Wisk 64 and decreases more for Tide 64. This makes more sense beceause if there are price changes for a 64 size product, people might feel like they're getting a better deal for Tide 128 which is double the size of Tide 64 but now "cheaper".  

# C 

```{r}
lm128_E<-lm(log(q_tide128) ~ log(p_tide128)+log(p_tide64) +log(p_wisk64) + week + factor(store), data = detergent_DF_2)
lm64_E<- lm(log(q_tide64) ~ log(p_tide128)+log(p_tide64) +log(p_wisk64) + week+ factor(store), data = detergent_DF_2)

lm128_Ea = tidy(lm128_E)
lm64_Ea = tidy(lm64_E)

kable(lm128_D[c(1:4),], digits = 4)
kable(lm128_Ea[c(1:4),], digits = 4)

kable(lm64_D[c(1:4),], digits = 4)
kable(lm64_Ea[c(1:4),], digits = 4)

```


Discussion:
How do the elasticity estimates and the time trend compare across these two regressions? Is the difference (or absence of a difference) as expected? 

They are surprisingly identical, using unit sales instead of velocity did not have any effect. This doesn't make sense conceptually, large stores and small stores should have variation between them. When we removed our velocity it did nothing to change the elasticities.


## Question 6

r = 25%
C = 0.25 / oz

Q128 = A128 * P128^(-2.3836) * P64^(0.2097) * PW64^(1.1648)
Q64 = A64 * P128^(0.9028) * P64^(-1.4867) * PW64^(-0.2809)

# A

```{r}
baseprice128 = mean(detergent_DF_2$p_tide128)
baseprice128
```

# B
```{r}
baseprice64 = mean(detergent_DF_2$p_tide64)
baseprice64
```

# C / D

```{r}
stores <- length(unique(detergent_DF_2$store))

basevolume128 = stores * 52 * mean(detergent_DF_2$q_tide128)
basevolume64 = stores * 52 * mean(detergent_DF_2$q_tide64)

basevolume128
basevolume64

```

# E

Base Profits:
pi128=Q_128*(P_128(1-r)-C)

```{r}
Bprofit128 = basevolume128 * ((baseprice128*0.75) - 0.25)
Bprofit64 = basevolume64 * ((baseprice64*0.75) - 0.25)

BaseTotalProfit <- Bprofit128 + Bprofit64
BaseTotalProfit

```


# F

Scenario1: 5% increase in price for both 128 and 64
Scenario2: 5% decrease in price for both 128 and 64
Scenario3: 5% increase in price 128 and 5% decrease in 64
Scenario4: 5% decrease in price 128 and 5% increase in 64

r = 25%
C = 0.25 / oz

Q128 = A128 * P128^(-2.3836) * P64^(0.2097) * PW64^(1.1648)
Q64 = A64 * P128^(0.9028) * P64^(-1.4867) * PW64^(-0.2809)


```{r}
pricechange = 0.05

# Specify the function
demand_change <- function(price_change1, price_change2, price_elasticity1, price_elasticity2, price_elasticity3, basequantity) {
   
   # New demand from method 1 
   quantity_change_1 = ((1 + price_change1)^price_elasticity1) * ((1 + price_change2)^price_elasticity2) *
      ((1)^price_elasticity3)
    
   #Get new quantity from ratio of new / old 
   
   NewQuantity = quantity_change_1 * basequantity
   
   # Return results as a list
   return(NewQuantity)
}

```

Running the Function
```{r}
New_Q128_1 <- demand_change(0.05, 0.05, -2.11, 0.211,1.1648, basevolume128)
New_Q64_1 <- demand_change(0.05,0.05,1.16,-1.585, -0.2809, basevolume64)

New_Q128_2 <- demand_change(-0.05, -0.05, -2.11, 0.211, 1.1648, basevolume128)
New_Q64_2 <- demand_change(-0.05,-0.05,1.16,-1.585 , -0.2809, basevolume64)

New_Q128_3 <- demand_change(0.05, 0.05, -2.11, 0.211, 1.1648, basevolume128)
New_Q64_3 <- demand_change(-0.05,-0.05,1.16,-1.585 , -0.2809, basevolume64)

New_Q128_4 <- demand_change(-0.05, -0.05, -2.11, 0.211, 1.1648, basevolume128)
New_Q64_4 <- demand_change(0.05,0.05,1.16,-1.585 , -0.2809, basevolume64)

```

# G
```{r}
#Total Profit calculations
TotalProfit1 <- (New_Q128_1* (baseprice128*1.05))*(New_Q64_1* (baseprice64*1.05))

TotalProfit2 <- (New_Q128_2*(baseprice128*0.95))*(New_Q64_2* (baseprice64*0.95))

TotalProfit3 <- (New_Q128_3*(baseprice128*1.05))*(New_Q64_3*(baseprice64*0.95))

TotalProfit4 <- (New_Q128_4*(baseprice128*0.95))*(New_Q64_4* (baseprice64*1.05))
```


: Table of quantities sold and profits when Tide changes the price of Tide 64 and 128. Price changes are shown in percentages

```{r}
library(scales)
del_price_128 = c(0.05, -0.05, 0.05, -0.05)
del_price_64 = c(0.05, -0.05, -0.05, 0.05)
q_128 = c(New_Q128_1, New_Q128_2, New_Q128_3, New_Q128_4)
q_64 = c(New_Q64_1, New_Q64_2, New_Q64_3, New_Q64_4)
TotalProfits = c(TotalProfit1, TotalProfit2, TotalProfit3, TotalProfit4)


Price_Change<- as.factor(paste('128',del_price_128,'64',del_price_64, sep = "|"))

NewTable <- data.frame(del_price_128, del_price_64, q_128, q_64,Price_Change, TotalProfits)

NewTable
plot(NewTable$Price_Change, NewTable$TotalProfits)
ggplot(data = NewTable, aes(Price_Change,TotalProfits))+geom_point(size=10,show.legend = NA)+scale_y_continuous(labels = comma)





```


## Question 7

a. What is the extent of cannibalization within the Tide product line? 
b. Does Tide face a competitive threat from Wisk? 
c. How do you evaluate the current pricing tactics? Do you recommend changes? 



```{r}
lm128
lm128_B
lm128_C
lm128_E

lm(formula = log(svelocity128) ~ log(p_tide128) + log(p_tide64), 
    data = dt)




```







