---
title: "Assignment 4"
author: "Caleb Aguiar and Annie Beyer"
date: "2/8/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Part I: Promotional event planning

## Is there evidence for strong seasonal demand for this product, based on the figures presented in the
“Event” sheet? (0.5 points) hint: The timing of events in the “Event” sheet are reported the “Promotion
calendar” sheet.

For Event 2, which occurs in December, the base cases is 1360, and for Event 1 which occurs in November, the base cases is 728. This is far larger than the base cases for other events during other times of the year.

## Expressed as a percentage of base sales, does event 1 or event 2 produce a greater incremental sales response? (0.5 points)

```{r}
Event_1_Percent<-paste(round((1129-728)/(1129), digits = 2), '%')

Event_2_Percent<-paste(round((2303-1360)/(2303), digits = 2), '%')

Promo_Table<-data.frame(Event_1_Percent,Event_2_Percent)

Promo_Table
```

