---
title: "Assignment 4"
author: "Caleb Aguiar and Annie Beyer"
date: "2/8/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Part I: Promotional event planning

## 1) Is there evidence for strong seasonal demand for this product, based on the figures presented in the “Event” sheet? (0.5 points) hint: The timing of events in the “Event” sheet are reported the “Promotion calendar” sheet.

For Event 2, which occurs in December, the base cases is 1360, and for Event 1 which occurs in November, the base cases is 728. This is far larger than the base cases for other events during other times of the year.

## 2) Expressed as a percentage of base sales, does event 1 or event 2 produce a greater incremental sales response? (0.5 points)

```{r}
Event_1_Percent<-paste(round((1129-728)/(1129), digits = 2), '%')

Event_2_Percent<-paste(round((2303-1360)/(2303), digits = 2), '%')

Promo_Table<-data.frame(Event_1_Percent,Event_2_Percent)

Promo_Table
```

## 3) Discuss the profitability results for these five events. Which events are most profitable and why? What can you learn from this analysis about what sorts of promotional events are most profitable? (0.5 points)


The most profitable events are Event 2 with an ROI of 44% and Event 5 with an ROI of 53%. 


## 4) Recalculate the profitability for event 1 and 2 assuming that retailers will engage in 4 weeks rather
than 2 weeks of forward buying. (0.5 points)

Specify functions

```{r}
#Incremental Contribution = Incremental Consumed Cases × VCM
Incremental_Contribution <- function(Incremental_Consumed_Cases, VCM) {
     
  Inc_Con <- Incremental_Consumed_Cases*VCM

   return(Inc_Con)
}

Variable_Cost <- function(Total_Consumed_Cases, Off_Invoice){
  Var_Cost<-Total_Consumed_Cases*Off_Invoice
  return(Var_Cost)
}

Forward_Buy_Cost<-function(Forward_Buy_Cases, Off_Invoice){
  For_Buy_Cst<-Forward_Buy_Cases*Off_Invoice
  return(For_Buy_Cst)
}

ROI_fun<-function(Event_Gross_Contribution,Event_Cost){
  ROI<-paste(round((100*(Event_Gross_Contribution/Event_Cost)),digits=1),"%")
  return(ROI)
}



```

Do calculations for Event 1 and Event 2

```{r}



Event_1_Inc_Con<-Incremental_Contribution(401,20)#I got VCM from Figure 1: Brand Summary 
Event_2_Inc_Con<-Incremental_Contribution(944,20)


Event_1_Var_Cost<-Variable_Cost(1129,4.2)
Event_2_Var_Cost<-Variable_Cost(2303,4.2)

wks_4_For<-458#Number purchased for four weeks of foward buying, (229/2)*4
Event_1_For_Buy_Cst<-Forward_Buy_Cost(wks_4_For,4.2)
Event_2_For_Buy_Cst<-Forward_Buy_Cost(wks_4_For,4.2)

Fixed_Payment_Cost<-2500#(MDF)

Event_1_Total_Cost<-Event_1_Inc_Con+Event_1_Var_Cost+Event_1_For_Buy_Cst+Fixed_Payment_Cost
Event_2_Total_Cost<-Event_2_Inc_Con+Event_2_Var_Cost+Event_2_For_Buy_Cst+Fixed_Payment_Cost


#Find out how many cases we have
ROI_Event_1<-ROI_fun(8019,Event_1_Total_Cost)
ROI_Event_2<-ROI_fun(18874,Event_2_Total_Cost)


```




## 5) Compare the approach to calculating the ROI that we took in class with the Booz Allen Hamilton
approach taken here (the difference was explained above). Is one of the approaches better than the
other, and why? (0.5 points) hint: consider a scenario where the margin is 50 cents and we are able to
sell 10 units, if we cut the price by 25 cents and the new margin is 25 cents, we are able to sell 20 units.
What is the “cost” of this promotion? Is it 10 (baseline units) times 25 cents (reduced margin) or is it
20 (baseline + incremental units) times 25 cents?




ROI = Change in Profit/Investment = ((P-C)*Change in Quantity - Investment)/Investment


```{r}
#Events 3-5 in case I need them.
Event_3_Inc_Con<-Incremental_Contribution(278,20)
Event_4_Inc_Con<-Incremental_Contribution(63,20)
Event_5_Inc_Con<-Incremental_Contribution(602,20)
```

