---
title: "Assignment $"
author: "Your name"
date: "1/1/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Upload and Explore Data

```{r}
load(file = "Detergent.RData")
dt <- detergent_DF
library(skimr)
skim(dt)
head(dt)
```

## Question 1

# A

```{r}
#Make Revenue column for each product

dt$T128Revenue <- dt$q_tide128 * dt$p_tide128
dt$T64Revenue <- dt$q_tide64 * dt$p_tide64
dt$WiskRevenue <- dt$q_wisk64 * dt$p_wisk64

TotalRevenue <- sum(dt$T128Revenue) + sum(dt$T64Revenue) + sum(dt$WiskRevenue)

T128Rev <- (sum(dt$T128Revenue) / TotalRevenue) * 100
T64Rev <- (sum(dt$T64Revenue) / TotalRevenue) * 100
WiskRev <- (sum(dt$WiskRevenue) / TotalRevenue) * 100

TotalRevenue1 <- format(round(TotalRevenue, 2), nsmall = 2)
T128Rev1 <- format(round(T128Rev, 2), nsmall = 2)
T64Rev1 <- format(round(T64Rev, 2), nsmall = 2)
WiskRev1 <- format(round(WiskRev, 2), nsmall = 2)

Mean128 <- mean(dt$p_tide128)
Mean64 <- mean(dt$p_tide64)
MeanW <- mean(dt$p_wisk64)

SD128 <- sd(dt$p_tide128)
SD64 <- sd(dt$p_tide64)
SDW <- sd(dt$p_wisk64)

Med128 <- median(dt$p_tide128)
Medn64 <- median(dt$p_tide64)
MednW <- median(dt$p_wisk64)

library(data.table)
MarketShare <- data.frame(Marketshare = c(T128Rev1, T64Rev1, WiskRev1),
                          MeanPrice = c(Mean128, Mean64, MeanW),
                          MedianPrice = c(Med128, Medn64, MednW),
                          Std.Dev = c(SD128, SD64, SDW))
                          
rownames(MarketShare) <- c("Tide 128 oz", "Tide 64 oz", "Wisk 64 oz")
MarketShare          
```

# B
Price Gap

```{r}
dt$PriceGap1 <- dt$p_tide128 - dt$p_tide64
dt$PriceGap2 <- dt$p_tide64 - dt$p_wisk64

MeanPG1 <- mean(dt$PriceGap1)
MeanPG2 <- mean(dt$PriceGap2)

SDPG1 <- sd(dt$PriceGap1)
SDPG2 <- sd(dt$PriceGap2)

MedPG1 <- median(dt$PriceGap1)
MedPG2 <- median(dt$PriceGap2)

PriceGap <- data.frame(MeanPriceGap = c(MeanPG1, MeanPG2),
                          MedianPriceGap = c(MedPG1, MedPG2),
                          Std.DevPriceGap = c(SDPG1, SDPG2))
                          
rownames(PriceGap) <- c("Tide128- Tide64", "Tide64 - Wisk64")
PriceGap  
```

# C
Hisotgrams
```{r}
hist(dt$PriceGap1, freq = F, col = "steelblue", breaks = 50, xlab = "Price Gap 1 ($)", main = "Price Gap of Tide 128 - Tide 64", xlim = c(0, 8))
hist(dt$PriceGap2, freq = F, col = "orange", breaks = 50, xlab = "Price Gap 2 ($)", main = "Price Gap of Tide 64 - Wisk 64", xlim = c(0, 8))

```


# D
Discussion:
What do you learn from the price gap histograms and summary statistics for your analysis above? 

Is there enough variation in the price gaps across stores and weeks to estimate the cross price elasticities
between the two Tide pack sizes and Wisk 64?


## Question 2

# A 
Sales velocity for Tide 128 and Tide 64

```{r}
dt$svelocity128 <- (dt$q_tide128/dt$acv)
dt$svelocity64 <- (dt$q_tide64/dt$acv)

SalesVelocity128 <- sum(dt$svelocity128)
SalesVelocity64 <- sum(dt$svelocity64)

SalesVelocity128
SalesVelocity64
```

# B
Discussion:
What is the purpose of dividing unit sales by ACV to construct the dependent variable?

Normalization? 


# C
Log linear demand model 
```{r}
lm128 = lm(log(svelocity128) ~ log(p_tide128)+log(p_tide64) + log(p_wisk64), data = dt)
lm64 = lm(log(svelocity64) ~ log(p_tide128)+log(p_tide64) + log(p_wisk64), data = dt)

summary(lm128)
summary(lm64)
```


# D
Discussion:
Discuss whether the demand estimates (own and cross price elasticities) make sense. Are the magnitudes
and signs of the estimated parameters as you would expect? 


## Question 3

# A
Time Trend - DO WE NEED TO FACTOR IT? THAT WOULD CREATE 299 DUMMY VARIABLES....

```{r}
lm128_B = lm(log(svelocity128) ~ log(p_tide128)+log(p_tide64) + log(p_wisk64) + log(week), data = dt)
lm64_B = lm(log(svelocity64) ~ log(p_tide128)+log(p_tide64) + log(p_wisk64) + log(week), data = dt)

summary(lm128_B)
summary(lm64_B)
```

# B
Discussion:
Explain why adding a time trend is important here. Discuss whether the demand estimates now make
sense. Is there an improvement over the model specification in question 2?



## Question 4

# A

195/300 weeks had at least one promotion

```{r}
library(dplyr)
detergent_promos <- dt %>% select(week, promoflag) %>% 
  filter(promoflag == 1)

detergent_promos

detergent_DF_2 = subset(detergent_DF, promoflag != 1)

```


# B

```{r}
detergent_DF_2$svelocity128 <- (detergent_DF_2$q_tide128/detergent_DF_2$acv)
detergent_DF_2$svelocity64 <- (detergent_DF_2$q_tide64/detergent_DF_2$acv)

SalesVelocity128_B <- sum(detergent_DF_2$svelocity128)
SalesVelocity64_B <- sum(detergent_DF_2$svelocity64)

lm128_C = lm(log(svelocity128) ~ log(p_tide128)+log(p_tide64) + log(p_wisk64) + log(week), data = detergent_DF_2)
lm64_C = lm(log(svelocity64) ~ log(p_tide128)+log(p_tide64) + log(p_wisk64) + log(week), data = detergent_DF_2)

summary(lm128_C)
summary(lm64_C)

```


# Discussion
Discuss whether the demand estimates (own and cross price elasticities) now make sense - is there an improvement over the specification in question 3? Provide some intuition for the change in the estimated own-price effects.


## Question 5

Store Fixed Effect

```{r}
lm128_D = lm(log(svelocity128) ~ log(p_tide128)+log(p_tide64) + log(p_wisk64) + log(week) + factor(store), data = detergent_DF_2)
lm64_D = lm(log(svelocity64) ~ log(p_tide128)+log(p_tide64) + log(p_wisk64) + log(week)+ factor(store), data = detergent_DF_2)

library(broom)
library(knitr)

lm128_D = tidy(lm128_D)
lm64_D = tidy(lm64_D)

kable(lm128_D[c(1:5),], digits = 4)
kable(lm64_D[c(1:5),], digits = 4)
```

# B
Discussion:
Do the estimates of own and cross price elasticties reveal an improvement over the model specification
in question 4? 


# C 

```{r}
lm128_E = lm(log(q_tide128) ~ log(p_tide128)+log(p_tide64) + log(p_wisk64) + log(week) + factor(store), data = detergent_DF_2)
lm64_E = lm(log(q_tide64) ~ log(p_tide128)+log(p_tide64) + log(p_wisk64) + log(week)+ factor(store), data = detergent_DF_2)

lm128_E = tidy(lm128_E)
lm64_E = tidy(lm64_E)

kable(lm128_E[c(1:5),], digits = 4)
kable(lm64_E[c(1:5),], digits = 4)
```


Discussion:
How do the elasticity estimates and the time trend compare across these two
regressions? Is the difference (or absence of a difference) as expected? (


## Question 6

r = 25%
C = 0.25 / oz

# A

```{r}
baseprice128 = mean(detergent_DF_2$p_tide128)

```

# B
```{r}
baseprice64 = mean(detergent_DF_2$p_tide64)
```

# C / D

```{r}
stores = 86

basevolume128 = stores * 52 * mean(detergent_DF_2$q_tide128)
basevolume64 = stores * 52 * mean(detergent_DF_2$q_tide64)

```

# E

Base Profits:
pi128=Q_128*(P_128(1-r)-C)

```{r}
Bprofit128 = basevolume128 * ((baseprice128*0.75) - 0.25)
Bprofit64 = basevolume64 * ((baseprice64*0.75) - 0.25)

BaseTotalProfit <- Bprofit128 + Bprofit64
BaseTotalProfit

```


# F





: Table of quantities sold and profits when Tide changes the price of Tide 64 and 128. Price changes are shown in percentages

+---------------+---------------+-------------+--------------+---------------+
| del_price_128 | del_price_64  | q_128       | q_64         | Total profits |          
+===============+===============+=============+==============+===============+
| 0.05          | 0.05          |             |              |               |
+---------------+---------------+-------------+--------------+---------------+
| -0.05         | -0.05         |             |              |               |
+---------------+---------------+-------------+--------------+---------------+
| 0.05          | -0.05         |             |              |               |
+---------------+---------------+-------------+--------------+---------------+
| -0.05         | 0.05          |             |              |               |
+---------------+---------------+-------------+--------------+---------------+
